Integrated farming and global warming mitigation in Brazil

### 2022-08-03 manuscript/manuscript.qmd
Update objectives. Add diagrams in the matherials section.

---
title: Integrated farming and global warming mitigation in Brazil
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
toc: true
toc-title: Contents
format: 
  html:
    theme: lux
page-layout: article
editor: visual
bibliography: references.bib
link-citations: true
abstract: "There is a high expectation in the reduction of liquid greenhouse gases in Brazil by the implementation of integrated crop-livestock-forestry systems. The foundation of such expectation relies in the hypothesis that these systems are capable of storing more above and below ground carbon, in relation to conventional farming systems, due to the presence of trees. However, that are not robust estimates about the potential of these systems to store carbon in a national scale, and usually point estimates are used to extrapolate carbon sequestration. In order to improve the representation of carbon sequestration by integrated crop-livestock-forestry systems, this project aims to use published data to develop a spatially explicit model to estimate carbon fluxes in Brazil."
---

```{r}
#| include: false
  library(nomnoml)
```

@@

1.  What are the management practices that lead to the best com- promise between carbon sequestration and financial revenue for agricultural land under ICLFS?

2.  Can indirect land-use and land-cover changes, especially land sparing under expansion of ICLFS, improve the net carbon budget of this agricultural system?

3.  Does the prioritization of the provision of ecosystem services other than carbon storage imply in changes of productivity of ICLFS?

4.  Can further expansion of ICLFS, beyond Brazil's NDC target, replace the afforestation targets pledged in the scientific literature for the tropics in terms of carbon storage, provision of ecosystem services and economic revenue?

@@

In order to achieve the proposed objective, the work will be divided in four major parts:

1.  ICLFS management scenario elaboration;

2.  Adaptation and application of the modeling framework to ICLFS;

3.  Estimate the carbon balance, ecosystem services, and economic evaluation based on outputs from modeling framework;

4.  Results consolidation and analysis;

```{nomnoml}
#| echo: false

# direction: down
# .box: dashed
[Start]-[Finish!]
[Finish!]-[<box>blablablablabla
           lablablablablablabla]

@@

>>>>

---
title: Integrated farming and global warming mitigation in Brazil
author: 
  - name: Hugo Tameirão Seixas
    email: seixas.hugo@protonmail.com
    url: hugotseixas.com
    affiliations:
      - name: State University of Campinas
toc: true
toc-title: Contents
format: 
  html:
    theme: lux
page-layout: article
bibliography: references.bib
link-citations: true
abstract: "There is a high expectation in the reduction of liquid greenhouse gases in Brazil by the implementation of integrated crop-livestock-forestry systems. The foundation of such expectation relies in the hypothesis that these systems are capable of storing more above and below ground carbon, in relation to conventional farming systems, due to the presence of trees. However, that are not robust estimates about the potential of these systems to store carbon in a national scale, and usually point estimates are used to extrapolate carbon sequestration. In order to improve the representation of carbon sequestration by integrated crop-livestock-forestry systems, this project aims to use published data to develop a spatially explicit model to estimate carbon fluxes in Brazil."
---

```{r}
#| include: false

library(DiagrammeR)
```

@@

The present work is composed by three main objectives, accompanied by parallel related questions:

1. Develop an overview about the ICLF experiments characteristics being conducted in Brazil;

    1.1. What is the productivity of each component of ICLF systems of different characteristics?

    1.2. What are the effects of ICLF systems over soils characteristcs?

    1.3. What are the management characteristics of ICLF systems?

    1.4. WHat is the economical revenue of ICLF systems?

    1.5. What is the pottential expansion of ICLF systems in Brazil?

2. Estimate the potential of ICLF systems to remove carbon from the atmosphere by 2030 and 2050;

    2.1. What are the ICLF system management characteristics that provide the best balance between carbon removal, productivity and financial revenue?

    2.2. What are the main factors that influence the carbon removal in the modelling framework?

    2.3. What is the pottential of the expansion of ICLF systems in the emissions reduction pledges made by Brazil?

3.  Evaluate the feasibility of the implementation of ICLF as a mean to reduce emissions, in relation to different perspectives of solutions to avoid climatic catastrophe;

    3.1. Does the expansionof ICLF systems taking into account equity and possible social impacts, as a public policy?

    3.2. The actual strategies to promote the adoption of ICLF systems are being effective?

@@

In order to achieve the proposed objective, the work will be divided in three major parts:

1. Overview of ICLF characteristics in Brazil;

2. Future projections and estimates of benefits generated by ICLF systems adoption;

3. Critical analysis of ICLF as a public policy to curb climate change;

```{r}
#| echo: false

grViz(
  "digraph {

  graph [layout = dot, rankdir = TD, nodesep = 0.9, ranksep = 0.3]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  edge [penwidth = 1.5]

  a [label = 'Systematic \n Review', xlabel = '1']
  b [label = 'Experts Survey', xlabel = '1']
  c [label = 'ICLF overview \n data set', xlabel = '1']
  d [label = 'Projections \n Scenarios', xlabel = '2']
  e [label = 'LULC \n Projections', xlabel = '2']
  f [label = 'Benefits \n Estimations', xlabel = '2']
  g [label = 'Targeted \n Review', xlabel = '3']
  h [label = 'Narrative \n Discussion', xlabel = '3']

  a -> c b -> c
  c -> d d -> e
  e -> f c -> f
  f -> h g -> h

  }"
)

@@

```{r}
#| include: false

grViz(
  "digraph {

  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]

  edge [penwidth = 1.5]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.9,
        fontsize = 12]

  a [label = 'Degraded \n Pastures']
  b [label = 'Temperature']
  c [label = 'Precipitation']
  d [label = 'Potential \n Evapotranspiration']
  e [label = 'Soil Texture']
  f [label = 'System \n Management']
  g [label = 'LULC/Management \n Time Series']
  h [label = 'Productivity']
  i [label = 'Litter']
  j [label = 'Decomposition Rates']
  k [label = 'Below Ground Carbon']
  l [label = 'Above Ground Carbon']
  m [label = 'Emissions']
  n [label = 'Carbon Balance']

    node [shape = ellipse,
        fontname = Helvetica,
        style = dashed,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  1 [label = 'LULC Model']
  2 [label = 'Soil Carbon Model']
  3 [label = 'Productivity Model']
  4 [label = 'Economic Model']

  a -> 1 f -> 1 1 -> g
  g -> 2 b -> 2 c -> 2 d -> 2 e -> 2 i -> 2 j -> 2 2 -> k h -> 2
  g -> 3 b -> 3 c -> 3 e -> 3 3-> h 3 -> i h -> i 2 -> l i -> l h -> m
  h -> 4
  k -> n l -> n m -> n

  }"
)

#### Projections scenarios

#### LULC projections

```{r}
#| echo: false

grViz(
  "digraph {

  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]

  edge [penwidth = 1.5]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.9,
        fontsize = 12]

  a [label = 'Degraded \n Pastures']
  b [label = 'System \n Management']
  c [label = 'LULC Scenarios']
  d [label = 'LULC/Management \n Time Series']

    node [shape = ellipse,
        fontname = Helvetica,
        style = dashed,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  1 [label = 'LULC Model']

  a -> 1 b -> 1 c -> 1 1 -> d

  }"
)

#### Benefits estimations

```{r}
#| echo: false

grViz(
  "digraph {

  graph [layout = dot, rankdir = LR, nodesep = 0.9, ranksep = 0.3]

  edge [penwidth = 1.5]

  node [shape = box,
        fontname = Helvetica,
        style = filled,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.9,
        fontsize = 12]

  a [label = 'LULC/Management \n Time Series']
  b [label = 'Temperature']
  c [label = 'Precipitation']
  d [label = 'Potential \n Evapotranspiration']
  e [label = 'Soil Texture']
  h [label = 'Productivity']
  i [label = 'Litter']
  j [label = 'Decomposition Rates']

  node [shape = ellipse,
        fontname = Helvetica,
        style = dashed,
        fontcolor = '#343a40'
        fillcolor = '#f7f7f9'
        penwidth = 1.5,
        width = 1.5,
        fontsize = 12]

  1 [label = 'Productivity Model']
  2 [label = 'Soil Carbon Model']
  3 [label = 'Economic Model']

  a -> 1 a -> 2 a -> 3

  b -> 1 c -> 1 d -> 1 e -> 1
  1 -> h 1 -> i

  b -> 2 c -> 2 d -> 2 e -> 2 j -> 2 i -> 2

  h -> 3

  }"
)

### Critical analysis
